UKB Models

### 2023-12-27 eda/ukb_curation-eda.Rmd
qc-ing features with centile score of 1

@@

ggplot(data=ukb_df, aes(x=log_age, y=GMV)) +
  geom_point(aes(color=sex), alpha=0.6)
ggplot(data=ukb_df, aes(x=age_days, y=GMV)) +
  geom_point(aes(color=sex), alpha=0.6)
```

>>>>

```{r}
ukb_df.ppt.qc <- ukb_df %>%
  dplyr::filter(participant %in% ppt.list)

ggplot(data=ukb_df, aes(x=log_age, y=GMV)) +
  geom_point(aes(color=sex), alpha=0.6) +
  geom_text(data=ukb_df.ppt.qc,
            aes(x=log_age, y=GMV, label=participant))

ggplot(data=ukb_df, aes(x=log_age, y=lh_CT_cuneus)) +
  geom_point(aes(color=sex), alpha=0.6) +
  geom_text(data=ukb_df.ppt.qc,
            aes(x=log_age, y=lh_CT_cuneus, label=participant)) +
  geom_hline(yintercept=median(ukb_df$lh_CT_cuneus) + 7*stats::mad(ukb_df$lh_CT_cuneus))

ggplot(data=ukb_df, aes(x=log_age, y=lh_CT_pericalcarine)) +
  geom_point(aes(color=sex), alpha=0.6) +
  geom_text(data=ukb_df.ppt.qc,
            aes(x=log_age, y=lh_CT_pericalcarine, label=participant)) +
  geom_hline(yintercept=median(ukb_df$lh_CT_pericalcarine) + 7*stats::mad(ukb_df$lh_CT_pericalcarine))

ggplot(data=ukb_df, aes(x=log_age, y=lh_Vol_parahippocampal)) +
  geom_point(aes(color=sex), alpha=0.6) +
  geom_text(data=ukb_df.ppt.qc,
            aes(x=log_age, y=lh_Vol_parahippocampal, label=participant)) +
    geom_hline(yintercept=median(ukb_df$lh_Vol_parahippocampal) + 7*stats::mad(ukb_df$lh_Vol_parahippocampal))

ggplot(data=ukb_df, aes(x=log_age, y=rh_CT_medialorbitofrontal)) +
  geom_point(aes(color=sex), alpha=0.6) +
  geom_text(data=ukb_df.ppt.qc,
            aes(x=log_age, y=rh_CT_medialorbitofrontal, label=participant)) +
  geom_hline(yintercept=median(ukb_df$rh_CT_medialorbitofrontal) + 7*stats::mad(ukb_df$rh_CT_medialorbitofrontal))
```

@@

ggplot(data=ukb_df, aes(x=age_days, y=GMV)) +
  geom_point(aes(color=sex), alpha=0.6)
```

looking into subj. with centiles = 1
